---
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, echo=FALSE, message=FALSE, warning=FALSE)
```

# Rik's build of simple terminal (st)

```{r fig.align='center'}
knitr::include_graphics("images/st.svg")
```

## Overview

Simple terminal (st) is part of suckless tools for desktop. It aims to be simple, extendable and lightweight, and this build is designed to integrate my workflow.

## Features

- Supports transparency (needs xcompgr or other compositor for X).
- Supports ligatures.
- Gapless drawings.
- Customizable via `.Xresources`. Default theme is gruvbox.
- Standalone scrollback terminal session history (up to $1 \cdot 10^5$ lines).
- Interacts with external scripts.
- Usual behavior of `DEL` key.

## Hotkeys

- `Alt+y`: Copy.
- `Alt+p`: Paste.
- `Alt+k`: Scroll up.
- `Alt+j`: Scroll down.
- `Alt+Shift+k`: Zoom in.
- `Alt+Shift+j`: Zoom out.
- `Alt+Shift+r`: Zoom reset.
- `Alt+l`: Copy link.
- `Alt+Shift+l`: Follow link.
- `Alt+o`: Copy output.
- `Alt+x`: Invert colorscheme.

## How to install

```{bash eval=FALSE, echo=TRUE}
git clone https://github.com/rikferreira/st.git
cd st
sudo make clean install
```

### Dependencies

These headers may appear in errors while trying to compile dwm:

```{c eval=FALSE, echo=TRUE}
#include <X11/Xlib.h>
#include <X11/Xft/Xft.h>
#include <X11/extensions/Xinerama.h>
```

The icons in the tag bar are from the `font-awesome` package.

#### Arch

```{bash eval=FALSE, echo=TRUE}
sudo pacman -S libx11 libxft libxinerama ttf-font-awesome
```

#### Debian

```{bash eval=FALSE, echo=TRUE}
sudo apt install libx11-dev libxft-dev libxinerama-dev fonts-font-awesome
```

Notice that are some bindings to scripts that aren't in this repository. You may want to remove those because they will look in your `$PATH` for an executable with their names and it may not work as expected. I reinforce that this is my personal build to this software and it is designed to work with other elements of my desktop.
